---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
title <- "Implications of kappa-casein evolutionary diversity for the self-assembly and stabilization of casein micelles"
authors <- "Jean Manguy and Denis C. Shields"
year <- "2019"
journal <- "in preparation"
doi_article <- ""
doi_zenodo <- "10.5281/zenodo.2587122"
```

# kappa-casein-evolution-paper

`r badger::badge_custom("R ≥", "3.5", color = "green")`
`r badger::badge_custom("Python ≥", "3", color = "green")`
`r badger::badge_doi(doi_zenodo, "blue")`
<!-- `r badger::badge_doi(doi_article, "red")` -->

This repository contains the data and code for our paper:

> `r authors`, (`r year`). _`r title`_. `r journal` <`r doi_article`>

This repository is archived on Zenodo: [DOI: `r doi_zenodo`](https://doi.org/`r doi_zenodo`)

## Analysis

The code for the figures and the output can be viewed in a web browser, download and open the file `figures_and_tables_paper.html`.

We use [{ProjectTemplate}](https://github.com/KentonWhite/ProjectTemplate) to manage the analysis. The code was tested only on Linux.

### Install dependencies

1. download IUPred2A from <https://iupred2a.elte.hu/download> and unzip the archive in `lib/iupred2a/` (non-commercial users only)
2. install R >= 3.5 and python >= 3
3. install R packages (see `session_info.txt`)


### Generates the figures only

1. go to root of this repository
2. run:

```{r eval=FALSE}
library(ProjectTemplate)
load.project()
```
### Run the rmarkdown file

#### With Rstudio

1. open this repository with Rstudio
2. open `figures_and_tables_paper.Rmd` from Rstudio
3. Click on `Run` > `run all` (or Ctrl+Alt+R)

#### Without Rstudio

Run in a unix shell

```{sh eval=FALSE}
R -e "rmarkdown::render('figures_and_tables_paper.Rmd')"
```

Funding

Partly funded by an Enterprise Ireland grant to Food for Health Ireland [TC2013001].
