---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Implications of kappa-casein evolutionary diversity for the self-assembly and stabilization of casein micelles

`r badger::badge_custom("R >=", "3.4.4", color = "green")`
`r badger::badge_custom("Python >=", "3", color = "green")`


This repository contains the code and data for the paper: "Implications of kappa-casein evolutionary diversity for the self-assembly and stabilization of casein micelles".

The code for the figures and the output can be viewed in a web browser, download and open the file `figures_and_tables_paper.html`.

## To run the analysis

We use ProjectTemplate to manage the analysis. The code was tested only on Linux.

### Install dependencies

1. download IUPred2A from <https://iupred2a.elte.hu/download> and unzip the archive in `lib/iupred2a/`
2. install R packages (see `packages.txt`)

### Generates the figures only

1. go to root of this repository

2. run:

```{r eval=FALSE}
library(ProjectTemplate)
load.project()
```
### Run the rmarkdown file

#### With Rstudio

1. open this repository with Rstudio
2. open `figures_and_tables_paper.Rmd` from Rstudio
3. Click on `Run` > `run all` (or Ctrl+Alt+R)

#### Without Rstudio

Run

```{sh eval=FALSE}
R -e "rmarkdown::render('figures_and_tables_paper.Rmd')"
```


## Citation

```
Paper in preparation
```
